High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-01 paper/main.tex
backing up notes on reverse inference section

\subsubsection*{Reverse inference}
top 10 strongest correlations for each level; identify endpoint nodes
(RBFs); make map (threshold at $\theta$-- \textbf{JRM NOTE: what
  threshold did you use, Lucy?}); decode using neurosynth (cite).

>>>>

\subsubsection*{Reverse inference}
copying from lucy's message on slack:
- for each order, compute the average (pairwise) correlations
- pick the 10 strongest (absolute value) correlations
- find the RBFs on the endpoints of those correlations (i.e. the features being correlated)
- make a map by summing together those (thresholded at 0.999) RBFs
- decode with neurosynth
- print out top 10 terms
